A Data-Driven Framework for Neural Field Modelling

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure6
Changed Figure9

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure6.pdf}
\end{center}
\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
\label{fig:Figure6}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure9.pdf} 
\end{center}
\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region).} 
\label{fig:Figure9}
\end{figure}

>>>>

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure6.pdf}
\end{center}
\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 150 runs. All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
\label{fig:Figure6}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure9.pdf} 
\end{center}
\caption{{\bf Error in the field reconstruction}. The mean of average RMSE of the estimated field over 150 realisations (solid line) and the 95~\% confidence interval (grey region).} 
\label{fig:Figure9}
\end{figure}
